Computing properties of independent sets by generic programming tensor networks \thanks{\funding{...}}

### 2021-09-09 paper/paper.tex
clean up

\section{Introduction}
\blue{overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009}, treewidth of 3-regular graphs ~\cite{Fomin2006},
branching algorithm~\cite{Tarjan1977,Robson1986}
}
In graph theory and combinatorics, there are many interesting but hard computational problems concerning properties of independent sets.
An independent set is a set of vertices in a graph where no two vertices are adjacent to each other.
More formally, given an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set that for any $u,v \in I$, there is no edge connecting $u$ and $v$ in $G$.
The problem of finding an independent set of the largest possible size, the maximum independent set (MIS), is a paradigmatic NP-complete problem~\cite{Hastad1996}.
The size of the MIS of a graph $G$ is called the independence number, denoted as $\alpha(G) \equiv \max_{I}|I|$.

@@

\section{Benchmarks and case studies}
\subsection{Performance benchmarks}
We run a sequential program benchmark on CPU Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz, and show the results in Figure~\ref{fig:benchmark}.
Tensor network contraction can be parallelized. When the element type is immutable, one can also run it on GPUs to speed up the computation.

>>>>

\section{Introduction}
\blue{overlap gap property~\cite{Gamarnik2013, Gamarnik2019}, independence polynomial at -1~\cite{Bousquet2008,Levit2009},
branching algorithm~\cite{Tarjan1977,Robson1986}
}
In graph theory and combinatorics, there are many interesting but hard computational problems concerning properties of independent sets.
An independent set is a set of vertices in a graph where no two vertices are adjacent to each other.
More formally, given an undirected graph $G = (V,E)$, an independent set $I \subseteq V$ is a set that for any $u,v \in I$, there is no edge connecting $u$ and $v$ in $G$.
The problem of finding an independent set of the largest possible size, the maximum independent set (MIS), is a paradigmatic NP-complete problem~\cite{Hastad1996}.
The size of the MIS of a graph $G$ is called the independence number, denoted as $\alpha(G) \equiv \max_{I}|I|$.

@@

\section{Benchmarks and case studies}
\subsection{Performance benchmarks}
We run a sequential program benchmark on CPU Intel(R) Core(TM) i5-10400 CPU @ 2.90GHz, and show the results in Figure~\ref{fig:benchmark}.
Tensor network contraction can be parallelized. When the element type is immutable, one can also run it on GPUs to speed up the computation.
The graph we use are random 3 regular graphs, a typical type of sparse graph that having small tree width $tw(G) \leq |V|/6$~\cite{Fomin2006}.
